Practical Open-Loop Optimistic Planning

### 2019-06-11 paper/main.tex
Updates from Overleaf

    \includegraphics[width=0.64\textwidth]{img/ODP_svg-tex}    \includegraphics[width=0.64\textwidth]{img/OLOP_svg-tex}
    \includegraphics[width=0.64\textwidth]{img/KL-OLOP_svg-tex}

>>>>

    \includegraphics[width=0.64\textwidth]{img/tree-ODP_svg-tex}    \includegraphics[width=0.64\textwidth]{img/tree-OLOP_svg-tex}
    \includegraphics[width=0.64\textwidth]{img/tree-KL-OLOP_svg-tex}

### 2019-06-11 paper/poster/poster.tex
Updates from Overleaf

% Other packages
\usepackage{tabularx}
\def\tabularxcolumn#1{m{#1}}
\def\imagetop#1{\vtop{\null\hbox{#1}}}
\usepackage{adjustbox}
\usepackage{subfig}
\usepackage{floatrow} % sidecapfloat
\usepackage{setspace}
\usepackage{xspace}
\usepackage{noReferences}
\usepackage{caption}
\usepackage{tikz}
\usepackage[customcolors]{hf-tikz}
%\usepackage{subcaption}
\usepackage{epsf}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{enumitem}
\usepackage{float}
\usepackage{cases}
\usepackage{verbatim}
\usepackage{array}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{multirow}
\usepackage{listings}
%\usepackage[authoryear]{natbib}
\usepackage{authblk}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{eqparbox}
\usepackage{xcolor}
\usepackage[backend=biber, citestyle=authoryear, maxcitenames=2, maxbibnames=2]{biblatex}

@@

@@

%\background{ % Set the background to an image (background.pdf)
%\begin{tikzpicture}[remember picture,overlay]
%\draw (current page.north west)+(-2em,2em) node[anchor=north west]
%{\includegraphics[height=1.1\textheight]{background.png}};
%\end{tikzpicture}
%}
\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
boxColorOne=boxcolor, % Background color for the content in the content boxes
headershape=roundedright, % Specify the rounded corner in the content box headers
%headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
headerfont=\Large\bf\textsc, %Sans Serif
textborder=rectangle,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain,
textfont={\setlength{\parindent}{0.0em}\sffamily},
headerheight={0.05\textheight},
eyecatcher=true
%columns=5
}
%
%----------------------------------------------------------------------------------------
%	Title and authors
%----------------------------------------------------------------------------------------
%
{
\includegraphics[width=14em]{./img/renault_group}
}
{
Approximate Robust Control of Uncertain\\Dynamical Systems
}
{
Edouard Leurent, Yann Blanco, Denis Efimov, Odalric-Ambrym Maillard
\vspace{-3\baselineskip}
}
{
\includegraphics[width=14em]{./img/inria_sc}
}

@@

\headerbox{\textsc{Motivation}}{name=motivation,span=1,column=0,row=0}{
\begin{center}
%\includegraphics[width=\textwidth]{../img/pipeline}    
\textbf{Decision-making} pipeline in Autonomous Driving
\end{center}

\textbf{Progress has been made} {\small \parencite{Paden2016}}
\begin{itemize}[nolistsep]
\item[$\eqgcolb{\blacktriangleright}$] \hlg{route planning} is solved
\item[$\eqbcolb{\blacktriangleright}$] reliable techniques exist for \hlb{motion planning} and \hlb{control}
\end{itemize}

\vspace{.5\baselineskip}
\textbf{Current limitations}
\begin{itemize}[nolistsep,leftmargin=0.55cm]
\item[$\eqrcolb{\blacktriangleright}$] Implementations rely on \hlr{hand-crafted rules} such as FSM
\item[] \incarrow tailored for \hlr{specific} cases, won't \hlr{scale} to complex scenes
\item[$\eqrcolb{\blacktriangleright}$] Social interactions are difficult to model explicitly:
\item[] \incarrow poor \hlr{negotiation} abilities, \hlr{"freezing robot"} problem
\end{itemize}

\vspace{.5\baselineskip}
\textbf{We frame the problem in a sequential learning setting}
}

%----------------------------------------------------------------------------------------
%	Setting
%----------------------------------------------------------------------------------------
\headerbox{\textsc{Reinforcement learning}}{name=setting,span=1,column=0,row=0,below=motivation}{

    \hlb{\textbf{Optimal}} control under \hlr{unknown} dynamics $T(s_{t+1} | s_t, a_t)$

    \begin{equation}
        \max_\pi \expectedvalue \underbrace{\left[\sum_{t=0}^\infty \gamma^t r(s_t, a_t) \condbar \hleg{a_t\sim\pi(s_t)}, \hler{s_{t+1}\sim T(s_t, a_t)}\right]}_{\text{policy return }R^T_\pi}
    \end{equation}

    \textbf{Model-free} methods directly optimize $\hleg{\pi(a_t | s_t)}$ through policy evaluation and policy improvement.
    \vspace{1em}

    \textbf{Model-based} methods
    \begin{enumerate}[itemsep=0pt]
        \item Learn a model for the dynamics $\hler{\hat{T}(s_t, a_t)}$
        \item (Planning) Leverage it to compute
        \begin{equation*}
        \max_\pi \expectedvalue \left[\sum_{t=0}^\infty \gamma^t r(s_t, a_t) \condbar \hleg{a_t\sim\pi(s_t)}, \hler{s_{t+1}\sim \hat{T}(s_t, a_t)}\right]
        \end{equation*}
    \end{enumerate}

    \begin{itemize}[nolistsep]
        \item[$\eqgcolb{\blacktriangleright}$] Better \hlg{sample efficiency}, \hlg{interpretability}
        \item[$\eqrcolb{\blacktriangleright}$] $\hler{\text{Model bias: }\hat{T} \neq T}$
    \end{itemize}

@@

%----------------------------------------------------------------------------------------
% Tools
%----------------------------------------------------------------------------------------
\headerbox{\textsc{Robust optimization}}
%{name=tools,column=2,span =2}
{name=tools,column=0,below=setting,span =1}
{
\begin{enumerate}[nolistsep]
    \item Build a \textbf{confidence region} $\bT$ around $\hler{T}$
    \begin{equation*}
    \forall T'\in \bT, \quad \probability(||\hler{T} - T'|| > \epsilon) < \delta
    \end{equation*}
    \item Plan \textbf{robustly} with respect to this ambiguity
    \begin{equation}
        \hleg{\max_{\pi}}\ \underbrace{\hler{\min_{T\in \bT}} \expectedvalue \sum_{t=0}^\infty \gamma^t r_t}_{v^r(\pi)} 
    \end{equation}
\end{enumerate}

\textbf{One-step} game between the planner and the environment:
\begin{itemize}[nolistsep]
    \item[1.] the \hlg{learner} reveals its policy $\hleg{\pi}$
    \item[2.] the \hlr{adversary} chooses the worst-case dynamics $T$
\end{itemize}

\begin{center}
    \hlb{\textbf{Assumption}}
\end{center}
We consider deterministic systems: $s_{t+1} = T(s_t, a_t)$

\begin{center}
\hlr{\textbf{Challenge}} 
\end{center}
How to optimize this objective?
\begin{itemize}[nolistsep]
    \item \hlg{Linear} system: $\mathcal{H}_\infty$ control, robust LQ
    \item \hlg{Finite} state-space: Robust Dynamic Programming
    \item \hlr{Non-linear continuous} system: ?
\end{itemize}

@@

%----------------------------------------------------------------------------------------
%	Discrete Ambiguity
%----------------------------------------------------------------------------------------
\headerbox{\textsc{Discrete ambiguity and tree-based planning}}{name=discrete,column=1,span=2}{
\vspace{-.25\baselineskip}

\begin{center}
    \hlb{\textbf{Assumption}}
\end{center}
The ambiguity set $\bT$ and the action space $\mathcal{A}$ are discrete and \textbf{finite}: $
 \hleb{\bT = \{T_m\}_{m\in[1, M]}} \quad \text{and} \quad \mathcal{A} = \{a_k\}_{k\in[1, K]}$

 We propose a robust version of \textbf{optimistic planning} for deterministic systems {\small \parencite{Hren2008}}

\begin{tabular}{>{\centering}p{0.63\textwidth}>{\centering}p{0.32\textwidth}}
\begin{minipage}[]{0.63\textwidth}
\bookboxx{
\begin{definition}
Given node $i\in\mathcal{T}$, define

\textbf{The robust value:}
$$v^r_i \eqdef \hleg{\vphantom{\min_{m\in[1, M]}}\max_{\pi \in i\mathcal{A^\infty}}} \hler{\min_{m\in[1, M]}} R^{T_m}_\pi$$

\textbf{The robust u-value:}
$$u_i^r(n) \eqdef
\begin{cases}
\hler{\min_{m\in[1, M]}} \sum_{t=0}^{d-1} \gamma^t r_t &\text{if } i \in \mathcal{L}_n \text{ ;}\\
\hleg{\max_{a\in\mathcal{A}}}\ u_{ia}^r(n) & \text{if } i \in \mathcal{T}_n \setminus \mathcal{L}_n
\end{cases}$$

\textbf{The robust b-value:}
$$b_i^r(n) \eqdef
\begin{cases}
\hler{\min_{m\in[1, M]}} \sum_{t=0}^{d-1} \gamma^t r_t + \frac{\gamma^d}{1-\gamma} &\text{if } i \in \mathcal{L}_n \text{ ;}\\
\hleg{\max_{a\in\mathcal{A}}}\ b_{ia}^r(n) & \text{if } i \in \mathcal{T}_n \setminus \mathcal{L}_n 
\end{cases}$$
\end{definition}
}

\bookboxx{
\begin{remark}[Ordering of min and max]
Naive comparison of action values between the different models do not recover the robust policy
%\includegraphics[width=\textwidth]{../img/min-max-order.eps}
\end{remark}
}

\bookboxx{
\begin{theorem}[Regret bound]
\label{theorem:drop-regret}
Algorithm \ref{algo:drop} enjoys a simple regret of:
\vspace{-0.5\baselineskip}
\begin{equation}
\text{If } \hler{\vph\kappa}>1,\qquad 
\hleb{\vph\mathcal{R}_n} = O\left(\hleg{\vph n}^{-\frac{\log 1/\gamma}{\log \hler{\vph\kappa}}}\right)
\end{equation}
\vspace{-\baselineskip}
\begin{equation}
\text{If }\hler{\vph\kappa}=1,\qquad
\hleb{\vph\mathcal{R}_n} = O\left(\gamma^{\frac{(1-\gamma)^\beta}{c}\hleg{\vph n}}\right)
\end{equation}
\vspace{-\baselineskip}
\end{theorem}
}
\end{minipage}

\begin{minipage}[]{0.32\textwidth}
\begin{center}
%\includegraphics[width=.95\textwidth]{../img/robust-control-tree}    
\end{center}

\textbf{Variables}
\begin{itemize}[nolistsep]
    \item[\incarrow] computational \hlg{budget $n$}
    \item[\incarrow] near-optimal \hlr{branching factor $\kappa$}
    \item[\incarrow] simple regret \hlb{$\mathcal{R}_n = v^r - v^r_{a(n)}$}
\end{itemize}
\vspace{\baselineskip}
\begin{normalsize}
\begin{algorithm}[H]
\DontPrintSemicolon
Initialize $\mathcal{T}$ to a root and expand it. Set $n=1$.\;
\While{Numerical resource available}{
Compute the robust u-values $u^r_i(n)$ and robust b-values $b^r_i(n)$.\;
Expand $\argmax_{i\in \mathcal{L}_n} b^r_i(n)$.\;
n = n + 1\;
}
\Return $a(n) = \argmax_{a\in \mathcal{A}} u^r_a(n)$
\caption{Deterministic Robust Optimistic Planning}
\label{algo:drop}
\end{algorithm}
\end{normalsize}

\end{minipage}
\end{tabular}
}

%----------------------------------------------------------------------------------------
%	Continuous Ambiguity
%----------------------------------------------------------------------------------------
\headerbox{\textsc{Continuous ambiguity and interval-based planning}}{name=continuous,span=2,column=1,below=discrete}{

\begin{tabular}[T]{cc}
\begin{minipage}{0.49\textwidth}
\hlr{\textbf{Approximate}} the robust objective by a \hlg{tractable} surrogate. \vspace{-0.5\baselineskip}
\bookboxx{
\begin{definition} Given a policy $\pi$ and current state $s_0$, define
\textbf{The reachability set} $S$ at time $t$: 
$$S(t, s_0, \pi) \eqdef \{s_t: \exists T \in \bT \text{ s.t. } s_{k+1} = T(s_{k}, \pi(s_{k}))\}$$

\textbf{The interval hull} {\small \parencite{Puig2005}}
$$\underline{s}(t, s_0, \pi) \eqdef \min S(t, s_0, \pi) \qquad \overline{s}(t, s_0, \pi) \eqdef \max S(t, s_0, \pi)$$
\end{definition}

\textbf{The surrogate objective} $\hat{v^r}$
\begin{equation}
\hleb{\vphantom{\frac{A}{A}}\hat{v^r}(\pi)} \eqdef \sum_{t=0}^H \gamma^t \min_{s\in \square S(t, s_0, \pi)}  r(s, \pi(s))
\end{equation}
}

The approximate performance of a policy is \hlg{guaranteed} on the true environment.
\vspace{-0.5\baselineskip}
\bookboxx{
\begin{proposition}[Lower bound]
\label{prop:lower-bound}
The surrogate objective $\hat{v^r}$ is a lower bound of the true objective $v^r$:

\begin{equation}
\forall \pi,\ \hleb{\vphantom{\frac{A}{A}}\hat{v^r}(\pi)} \leq \hler{\vphantom{\frac{A}{A}}v^r(\pi)}
\end{equation}
\end{proposition}
}

\end{minipage}

\begin{minipage}{0.47\textwidth}

\centering
%\includegraphics[width=0.7\textwidth]{../img/interval-hull}

\begin{footnotesize}
\begin{algorithm}[H]
  \SetAlgoLined\DontPrintSemicolon
  \SetKwFunction{algo}{robust\_control}\SetKwFunction{proc}{evaluate}
  \SetKwProg{myalg}{Algorithm}{}{}
  \myalg{\algo{$s_0$}}{
  Initialize a set $\Pi$ of policies\;
  \While{resources available}
  {
  \proc{} each policy $\pi\in\Pi$ at current state $s_0$\; 
  Update $\Pi$ by policy search\;  
  }
  \KwRet $\argmax_{\pi\in\Pi} \hleb{\hat{v^r}(\pi)}$ \;}{}
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\proc{$\pi$, $s_0$}}{
  \KwRet \hlb{$\hat{v^r}(\pi)$}\;}
\caption{Interval-based Robust Control}
\label{algo:irc}
\end{algorithm}
\end{footnotesize}
\end{minipage}
\end{tabular}

\vspace{.75\baselineskip}
}

%
%%----------------------------------------------------------------------------------------
%% Experiments
%%----------------------------------------------------------------------------------------
%
\headerbox{Experiments}{name=experiments,span=2,column=1,below=continuous, above=bottom}{

We introduce \textsc{highway-env}, a new environment for simulated highway driving and tactical decision-making\footnote{Video and source code are available at https://eleurent.github.io/robust-control/}.

In these experiments, the \hlg{ego-vehicle} is approaching a roundabout with
\hly{flowing traffic}.

We first consider ambiguity with respect to the possible \hlr{destination} of each vehicle (fig \subref*{fig:destination}), and then \wrt their \hlr{driving style} (fig \subref*{fig:driving-style}).

\begin{figure}[H] 
  \centering 
  \begin{tabular}{l}
  \subfloat[Discrete ambiguity]{\adjustbox{raise=-3.6pc}{
  %\includegraphics[width=0.27\textwidth]{../img/he-discrete.png}
  }\label{fig:destination}}\ 
  \subfloat[Continuous ambiguity]{\adjustbox{raise=-3.6pc}{
  %\includegraphics[width=0.27\textwidth]{../img/he-interval.png}
  \label{fig:driving-style}}}\
    \subfloat[Results]{
        \begin{tabular}{c c c c} \toprule
         Ambiguity & Agent & Worst-case & Mean $\pm$ std  \\ \midrule
         None & Oracle & $9.83$ & $10.84 \pm 0.16$ \\ \midrule
        \multirow{2}{*}{Discrete} & Nominal & $\hler{\vph 2.09}$ & $8.85 \pm 3.53$ \\
         & Algorithm \ref{algo:drop} & \textbf{$\hleg{\vph 8.99}$} &  \textbf{$10.78 \pm 0.34$} \\ \midrule
        \multirow{2}{*}{Continuous} & Nominal & $\hler{\vph 1.99}$ & $9.95 \pm 2.38$ \\
         & Algorithm \ref{algo:irc} & \textbf{$\hleg{\vph 7.88}$} & \textbf{$10.73 \pm 0.61$} \\ \bottomrule
         \end{tabular}
      }
  \end{tabular}
\end{figure}
}

%----------------------------------------------------------------------------------------
%	Acknowledgements
%----------------------------------------------------------------------------------------
\headerbox{Acknowledgements}{name=ack,column=0,span=1,below=tools}{
This work has been supported by CPER Nord-Pas de Calais/FEDER DATA Advanced data science and technologies 2015-2020, the French Ministry of Higher Education and Research, INRIA, and the French Agence Nationale de la Recherche (ANR).
}

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------
\headerbox{References}{name=refs,column=0,span=1,below=ack, above=bottom}{
    {
    \AtNextBibliography{\footnotesize}
    \setlength{\bibitemsep}{3pt}
    \printbibliography[heading=none]
    }
}

>>>>

% Other packages
\usepackage{tabularx}
\def\tabularxcolumn#1{m{#1}}
\def\imagetop#1{\vtop{\null\hbox{#1}}}
\usepackage{adjustbox}
\usepackage{subfig}
\usepackage{floatrow} % sidecapfloat
\usepackage{setspace}
\usepackage{xspace}
\usepackage{noReferences}
\usepackage{caption}
\usepackage{tikz}
\usepackage[customcolors]{hf-tikz}
%\usepackage{subcaption}
\usepackage{epsf}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{enumitem}
\usepackage{float}
\usepackage{cases}
\usepackage{verbatim}
\usepackage{array}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{multirow}
\usepackage{listings}
%\usepackage[authoryear]{natbib}
\usepackage{authblk}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{eqparbox}
\usepackage{xcolor}
\usepackage[backend=biber, citestyle=authoryear, maxcitenames=2, maxbibnames=2]{biblatex}
\usepackage{lipsum}
\usepackage{svg}

@@

% Removed from mathdef because of conflict with paper lcns class
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{property}{Property}

@@

%\background{ % Set the background to an image (background.pdf)
%\begin{tikzpicture}[remember picture,overlay]
%\draw (current page.north west)+(-2em,2em) node[anchor=north west]
%{\includegraphics[height=1.1\textheight]{background.png}};
%\end{tikzpicture}
%}
\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
boxColorOne=boxcolor, % Background color for the content in the content boxes
headershape=roundedright, % Specify the rounded corner in the content box headers
%headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
headerfont=\Large\bf\textsc, %Sans Serif
textborder=rectangle,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain,
textfont={\setlength{\parindent}{0.0em}\sffamily},
headerheight={0.05\textheight},
eyecatcher=true
%columns=5
}
%
%----------------------------------------------------------------------------------------
%	Title and authors
%----------------------------------------------------------------------------------------
%
{
\includegraphics[width=14em]{./img/renault_group}
}
{
Practical Open-Loop Optimistic Planning
}
{
Edouard Leurent, Odalric-Ambrym Maillard
\vspace{-3\baselineskip}
}
{
\includegraphics[width=14em]{./img/inria_sc}
}

@@

\headerbox{\textsc{Motivation}}{name=motivation,span=1,column=0,row=0}{

We consider the optimal control of an MDP $\cM = (\cS, \cA, R, T, \gamma)$ with bounded rewards $R$
\begin{itemize}
    \item $R$ and $T$ are \hlr{unknown}
    \item Access to a \hlb{generative model} $s' \sim \probability{s'|s,a}$ and $r\sim\probability{r|s, a}$
    \item \hlr{Fixed-budget} setting: the generative model can be queried $n$ times
\end{itemize}
}

%----------------------------------------------------------------------------------------
%	Setting
%----------------------------------------------------------------------------------------
\headerbox{\textsc{Open-Loop Optimistic Planning}}{name=setting,span=1,column=0,row=0,below=motivation}{
\OLOP algorithm introduced in [\cite{Bubeck2010}].

Split the budget $n$ into $M$ sequences of length $L$.
%Let $M$ be the largest integer such that $M \log M/(2 \log 1/\gamma) \leq n$\;
%Let $L = \log M / (2 \log 1/\gamma)$\;

\includesvg[width=\textwidth]{img/olop-explain.svg}
\includesvg[width=\textwidth]{img/olop-explain-2.svg}

\begin{center}
\begin{algorithm}[H]
\DontPrintSemicolon
\footnotesize
\For{each episode $m = 1, \cdots, M$}{
Compute $U_a(m-1)$ from \eqref{eq:Ua} for all $a\in\mathcal{T}$\;
Compute $B_a(m-1)$ from \eqref{eq:Ba} for all $a\in A^L$\;\label{alg:b_values_compute}
Sample a sequence with highest B-value: $a^m \in \argmax_{a\in A^L} B_a(m-1)$.\;
}
\Return the most played sequence $a(n) \in \argmax_{a\in A^L} T_a(M)$
\caption{General structure for Open-Loop Optimistic Planning}
\label{algo:kl-olop}
\end{algorithm}
\end{center}

@@

%----------------------------------------------------------------------------------------
% Tools
%----------------------------------------------------------------------------------------
\headerbox{\textsc{What's wrong with OLOP?}}
{name=tools,column=0,below=setting,span =1}
{

Overly pessimistic, especially in the low-budget regime.

\begin{equation}
         U^{\mu}_a(m) = \hat{\mu}_a(m) + \sqrt{\frac{2 \log M}{T_a(m)}}
    \end{equation}
    \begin{equation}
    \label{eq:Ua}
        U_a(m) \eqdef \sum_{t = 1}^h \gamma^t U^{\mu}_{a_{1:t}}(m) + \frac{\gamma^{h+1}}{1-\gamma}
    \end{equation}
    \begin{equation}
    \label{eq:Ba}
        B_a(m) \eqdef \inf_{1 \leq t \leq L} U_{a_{1:t}}(m)
    \end{equation}
    Intuitive explanation: 
    \begin{itemize}
        \item Unintended behaviour happens when $\hler{U^{\mu}_a(m) > 1}, \forall a$. 
        \item Then the sequence $(U_{a_{1:t}}(m))_t$ is non-decreasing
        \item Then \hlr{$B_a(m) = U_{a_{1:1}}(m)$}
    \end{itemize}

\includesvg[width=\textwidth]{img/olop-explain-3.svg}

\begin{center}
\texttt{OLOP} behaves as \hlr{uniform planning}!    
\end{center}
}

%----------------------------------------------------------------------------------------
%	KL-OLOP
%----------------------------------------------------------------------------------------
\headerbox{\textsc{Kullback-Leibler OLOP}}{name=klolop,column=1,span=2}{

\begin{minipage}[]{0.59\textwidth}
 We summon the upper-confidence bound from \texttt{kl-UCB} [\cite{Cappe2013}]:
    \begin{equation*}
        U^{\mu}_a(m) \eqdef \max \left\{q\in I: T_a(m) d(\hat{\mu}_a(m), q) \leq f(m) \right\}
    \end{equation*}

    \begin{center}
    \begin{tabular}{ccc}
    \toprule
        Algorithm & \texttt{OLOP} & \texttt{KL-OLOP} \\
        \midrule
        Interval $I$ & $\mathbb{R}$ & [0, 1] \\
        Divergence $d$ & $d_{\texttt{QUAD}}$ & $d_{\texttt{BER}}$ \\
        $f(m)$ & $4 \log M$ & $2\log M + 2 \log\log M$\\
        \bottomrule
    \end{tabular}
    \end{center}
    with
    \begin{align*}
    d_{\texttt{QUAD}}(p,q) &\eqdef 2(p-q)^2\\
    d_{\texttt{BER}}(p, q) &\eqdef p \log \frac{p}{q} + (1-p)\log\frac{1-p}{1-q}
    \end{align*}
\end{minipage}
\begin{minipage}[]{0.4\textwidth}
    \includegraphics[width=\textwidth]{../img/ukl}
\end{minipage}

Conversely,
\begin{itemize}
    \item \hlg{$U^{\mu}_a(m) \in I = [0, 1], \forall a$}. 
    \item The sequence $(U_{a_{1:t}}(m))_t$ is \hlg{non-increasing}
    \item $B_a(m) = U_a(m)$, the \emph{bound sharpening} step is \hlb{superfluous}.
\end{itemize}
}

%----------------------------------------------------------------------------------------
%	Sample Complexity
%----------------------------------------------------------------------------------------
\headerbox{Sample complexity}{name=sample,span=2,column=1,below=klolop}{ 
\begin{theorem}[Sample complexity]
\label{thm:regret}
\KLOLOP enjoys the same asymptotic regret bounds as \OLOP. More precisely, \KLOLOP satisfies:
\begin{equation*}
    \expectedvalue r_n = \begin{cases}
      \tilde{0}\left(n^{-\frac{\log 1/\gamma}{\log \kappa'}}\right), & \text{if}\ \gamma\sqrt{\kappa'} > 1 \\
      \tilde{0}\left(n^{-\frac{1}{2}}\right), & \text{if}\ \gamma\sqrt{\kappa'} \leq 1
    \end{cases}
\end{equation*}
\end{theorem}
}

%----------------------------------------------------------------------------------------
%	Time and Memory Complexity
%----------------------------------------------------------------------------------------
\headerbox{Time and memory complexity}{name=time,span=2,column=1,below=sample}{

\begin{tabular}{>{\centering}p{0.45\textwidth}>{\centering}p{0.5\textwidth}}
\begin{minipage}[]{0.45\textwidth}

\textbf{Original \KLOLOP}

\emph{Compute $B_a(m-1)$ from \eqref{eq:Ba} \hlr{for all $a\in A^L$}}

\textbf{Lazy \KLOLOP}
\begin{center}
\includegraphics[width=0.8\textwidth]{../img/tree_svg-tex}    
\end{center}

\begin{theorem}[Consistency]
\label{thm:consistency}
Algorithm \ref{algo:lazy-kl-olop} is \hlg{identical} to Algorithm \ref{algo:kl-olop}.
\end{theorem}
\end{minipage}

\begin{minipage}{0.5\textwidth}
    \begin{algorithm}[H]
\DontPrintSemicolon
\footnotesize
Let $\Tau_0^+ = \LL_0^+ = \{\emptyset\}$\;
\For{each episode $m = 1, \cdots, M$}{
Compute $U_a(m-1)$ from \eqref{eq:Ua} for all \hlg{$a\in\Tau_{m-1}^+$}\;
Compute $B_a(m-1)$ from \eqref{eq:Ba} for all \hlg{$a\in \LL_{m-1}^+$}\;
Sample a sequence with highest B-value: $a \in \argmax_{\hleg{a\in \LL_{m-1}^+}} B_a(m-1)$\;
Choose an arbitrary continuation $a^m \in aA^{L-|a|}$\tcp*[h]{e.g. uniformly}
Let $\Tau_m^+ = \Tau_{m-1}^+$ and $\LL_m^+ = \LL_{m-1}^+$\;
\For{$t=1, \cdots, L$}{
    \If{$a^m_{1:t} \not \in \Tau_{m}^+$}{
    \hlb{Add $a^m_{1:t-1}A$ to $\Tau_{m}^+$ and $\LL_{m}^+$}\;
    \hlb{Remove $a^m_{1:t-1}$ from $\LL_{m}^+$}
    }
}
}
\Return the most played $a(n) \in \argmax_{a\in \LL_m^+} T_a(M)$
\caption{Lazy Open Loop Optimistic Planning}
\label{algo:lazy-kl-olop}
\end{algorithm}
\end{minipage}
\end{tabular}

\begin{property}[Time and memory complexity]
\begin{equation*}
    \frac{C(\texttt{Lazy KL-OLOP})}{C(\texttt{KL-OLOP})} = \frac{\hleg{nK}}{\hler{K^{L}}}
\end{equation*}
\end{property}

@@

%
%%----------------------------------------------------------------------------------------
%% Experiments
%%----------------------------------------------------------------------------------------
%
\headerbox{Experiments}{name=experiments,span=2,column=1,below=time, above=bottom}{

\textbf{Expanded trees} for a budget $n=10^3$

    \includesvg[width=0.33\textwidth]{../img/tree-ODP}    \includesvg[width=0.33\textwidth]{../img/tree-OLOP}
    \includesvg[width=0.33\textwidth]{../img/tree-KL-OLOP}

\textbf{Average return} over 100 runs –- along with its 95\% confidence interval –- with respect to the available budget $n$

     \includesvg[width=0.33\textwidth]{../img/hw_return}
     \includesvg[width=0.33\textwidth]{../img/gw_return}
     \includesvg[width=0.33\textwidth]{../img/gw_stoch_return}
}

%----------------------------------------------------------------------------------------
%	Acknowledgements
%----------------------------------------------------------------------------------------
% \headerbox{Acknowledgements}{name=ack,column=0,span=1,below=tools}{
% This work has been supported by CPER Nord-Pas de Calais/FEDER DATA Advanced data science and technologies 2015-2020, the French Ministry of Higher Education and Research, INRIA, and the French Agence Nationale de la Recherche (ANR).
% }

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------
\headerbox{References}{name=refs,column=0,span=1,below=tools, above=bottom}{
    {
    \AtNextBibliography{\footnotesize}
    \setlength{\bibitemsep}{3pt}
    \printbibliography[heading=none]
    }
}
